\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-11 paper.tex
ELMo: Embedding from Language Model

This model is highly similar to \textbf{Word2Vec} introduced above.

\subsection{ELMo}
\subsection{BERT}
\section{Question Answering}

>>>>

This model is highly similar to \textbf{Word2Vec} introduced above. The only difference is \textbf{Word2Vec} looks for limited set of context surrounding the certain word, while \textbf{GloVe} calculates based on the whole document. Its training is performed on aggregated global word-word co-occurrence statistics from the corpus. Therefore, \textbf{GloVe} can only be offline, which is its main drawback. \\\\
This algorithm isn't used that frequently as the relevance between a word and its whole document is quite limited.

\subsection{Embedding from Language Model (ELMo)}
All the above models does not consider words with multiple meanings. Peters published a paper in 2018 of deep contextualized word representation that models complex characteristics of word use and how these uses vary across linguistic context. \\\\
Remarkably, previous models, after training, get constant vectors, while \textbf{ELMo} only gets a pre-trained vector. And the final output will be calculated after fine-tuning. So \textbf{ELMo} changes NLP from static to dynamic! \\\\
Given a sequence of $N$ tokens, $(t_1, t_2, t_3, ... t_N)$, we propose a forward language model that computes the probabilities of the sequence $t_k$ given all the history token $(t_1, t_2, t_3, ... t_k)$. 
\begin{align*}
p(t_1, t_2, t_3, ... t_N) = \prod^N_{k = 1} p(t_k | t_1, t_2, ... ,t_{k-1})
\end{align*}
The forward: \textbf{ELMo} uses LSTM layer to compute output. At the forward direction, for each position $k$, each LSTM layer outputs a context dependent representation $\vec{\mathbf{h}^{L,M}_{k, j}}$
\subsection{Bidirectional Encoder Representation from Transformer (BERT)}

\section{Question Answering}
